CRUSE to Safe Cycling in Ireland \\\large{An Open Source Methodology to Support Active Travel}

### 2023-09-22 paper.qmd
Finish UI section

The CRUSE web application is statically hosted, meaning that it can be accessed without the need for a server running software such as the R package 'shiny' or Python packages such as 'streamlit' or 'flask' in the background [@wickham2021].

>>>>

The CRUSE web application is statically hosted, meaning that it can be accessed without the need for a server running software such as the R package 'shiny' or Python packages such as 'streamlit' or 'flask' in the background [@wickham2021].
Typical intended user stories are illustrated in @fig-user-stories, which shows that the tool is designed to be used by both professional and non-professional users.
For the main target audience, professional transport planners working at the county level, the tool provides a range of outputs, including estimates of cycling potential at the county and network level.
The provision of balanced (the default), quietest and fastest route networks enables planners to consider the trade-offs between directness and 'cycle friendliness' when planning new infrastructure.
The tool also provides data downloads, enabling estimates of cycling potential on the network to be visualised and analysed with other tools such as QGIS, Python or R.

For non-professional users, the tool provides a simple interface to explore the cycling potential of the network.
By providing a single landing page that is suitable for both professional and non-professional users, the tool aims to facilitate communication between these groups.

```{mermaid}
%%| fig-width: 100%
%%| fig-cap: User stories for the CRUSE tool
%%| label: fig-user-stories
graph LR
    A(Professional user) --> B[CRUSE landing page]
    B --> C[CRUSE national map]
    C --> D[CRUSE county map]
    D --> F[Full county map]
    D --> CS[County statistics]
    D --> Q[Quiet and fast route networks]
    D --> DD[Data downloads]
    DD --> EX{External tools}
    X(Non-professional user) --> Y[CRUSE landing page]
    Y --> Z[CRUSE national map]
    Z --> R[CRUSE county level results]
    Z --> E(Exploration)
    R --> E
    E --> COMS{Communication}
```

### 2023-09-22 paper.tex
Finish UI section

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, boxrule=0pt, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

The methods used to generate the evidence presented in the CRUSE tool
for Ireland build on the Propensity to Cycle Tool (PCT), which was
originally funded by the UK's Department for Transport and developed by
a multi-university team. An important feature of the PCT is that it is
open source and publicly available (at
\href{https://www.pct.bike/}{www.pct.bike}), allowing its use by all
stakeholders in the transport planning process \citep{lovelace2017}. The
PCT approach has had major policy impacts, as outlined in Research
Excellence Framework (REF) impact case studies, which demonstrate that
the tool ``revolutionised strategic cycle planning in England and
Wales''\footnote{See REF Impact Case Study ``Cycle network policy,
  planning and investment transformed by the Propensity to Cycle Tool''
  at
  \href{https://results2021.ref.ac.uk/impact/847d1191-7f25-46ba-a399-b481125edc8f}{results2021.ref.ac.uk}
  submitted by the University of Leeds.} by overcoming the barriers to
cycling investment imposed by lack of evidence on cycling
potential\footnote{See the REF Impact Case Study ``Creating Step Changes
  in Cycling Policy and Infrastructure Planning across the UK'' at
  \href{https://results2021.ref.ac.uk/impact/4BBF3436-FD10-4C75-9791-F5E98AB4411B}{results2021.ref.ac.uk}
  submitted by the University of Westminster.}.

@@

However, travel to school and work only constitute a small proportion of
all trips. To overcome this issue, we developed a spatial interaction
modelling methodology to estimate the number of trips between each OD
pair for additional trip purposes.

The classification of trip purposes used in the CRUSE tool was guided
mainly by the trip purpose classification found within the National
Household Travel Survey (NHTS), but with the addition of categories
based on the comprehensive POWSCAR data, and the need to include
recreational trips and multi-stage trips (not yet implemented). An
overview of the trip purposes used in CRUSE is presented in
Figure~\ref{fig-trip-purposes}.

@@

>>>>

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

The methods used to generate the evidence presented in the CRUSE tool
for Ireland build on the Propensity to Cycle Tool (PCT), which was
originally funded by the UK's Department for Transport and developed by
a multi-university team. An important feature of the PCT is that it is
open source and publicly available (at
\href{https://www.pct.bike/}{www.pct.bike}), allowing its use by all
stakeholders in the transport planning process \citep{lovelace2017}. The
PCT approach has had major policy impacts, as outlined in Research
Excellence Framework (REF) impact case studies, which demonstrate that
the tool ``revolutionised strategic cycle planning in England and
Wales''\footnote{See REF Impact Case Study ``Cycle network policy,
  planning and investment transformed by the Propensity to Cycle Tool''
  at
  \href{https://results2021.ref.ac.uk/impact/847d1191-7f25-46ba-a399-b481125edc8f}{results2021.ref.ac.uk}
  submitted by the University of Leeds.} by overcoming the barriers to
cycling investment imposed by lack of evidence on cycling
potential\footnote{See the REF Impact Case Study ``Creating Step Changes
  in Cycling Policy and Infrastructure Planning across the UK'' at
  \href{https://results2021.ref.ac.uk/impact/4BBF3436-FD10-4C75-9791-F5E98AB4411B}{results2021.ref.ac.uk}
  submitted by the University of Westminster.} .

@@

However, travel to school and work only constitute a small proportion of
all trips. To overcome this issue, we developed a spatial interaction
modelling methodology to estimate the number of trips between each OD
pair for additional trip purposes. The classification of trip purposes
used in the CRUSE tool was guided mainly by the trip purpose
classification found within the National Household Travel Survey (NHTS),
but with the addition of categories based on the comprehensive POWSCAR
data, and the need to include recreational trips and multi-stage trips
(not yet implemented). An overview of the trip purposes used in CRUSE is
presented in Figure~\ref{fig-trip-purposes}.

@@

The CRUSE web application is statically hosted, meaning that it can be
accessed without the need for a server running software such as the R
package `shiny' or Python packages such as `streamlit' or `flask' in the
background \citep{wickham2021}. Typical intended user stories are
illustrated in Figure~\ref{fig-user-stories}, which shows that the tool
is designed to be used by both professional and non-professional users.
For the main target audience, professional transport planners working at
the county level, the tool provides a range of outputs, including
estimates of cycling potential at the county and network level. The
provision of balanced (the default), quietest and fastest route networks
enables planners to consider the trade-offs between directness and
`cycle friendliness' when planning new infrastructure. The tool also
provides data downloads, enabling estimates of cycling potential on the
network to be visualised and analysed with other tools such as QGIS,
Python or R.

For non-professional users, the tool provides a simple interface to
explore the cycling potential of the network. By providing a single
landing page that is suitable for both professional and non-professional
users, the tool aims to facilitate communication between these groups.

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-latex/mermaid-figure-1.png}

\caption{\label{fig-user-stories}User stories for the CRUSE tool}
